TESSELLATE asteroids paper

### 2025-09-11 PaperDraft/paperDraft.tex
added a few numbers

\red{57426} of asteroids with $V\leq \qty{20}{\mag}$ were found in the year 3 sectors we analysed.
Most of these are too faint for the lightcurve to give a reliable and period, while \citet{Pal2018} thinks good photometry down to $V\lesssim \qty{19}{\mag}$ should be achievable, we find the limit for \tessellate\ is closer to $m_{T} \approx \qty{17}{\mag}$ \citepalias{TESSELLATE}.
Once the quality checks (described above) have been applied, we are left with \red{4328} of planetesimals with accurate rotation rates.
\red{Some fraction} of these asteroids are not in the LCDB,%TODO check defind before
so we are the first to get the rotation period for these bodies.

@@

%TODO table of asteroids by class and frac that pass.

>>>>

\red{57426} of asteroids with $V\leq \qty{20}{\mag}$ were found in the year 3 sectors we analysed.
Most of these are too faint for the lightcurve to give a reliable and period, while \citet{Pal2018} thinks good photometry down to $V\lesssim \qty{19}{\mag}$ should be achievable, we find the limit for \tessellate\ is closer to $m_{T} \approx \qty{17}{\mag}$ \citepalias{TESSELLATE}.
Once the quality checks (described above) have been applied, we are left with \red{4328} of planetesimals with accurate rotation rates.
\red{\qty{80}{\percent}} of these asteroids do not have reliable periods reported in the LCDB, %TODO check defind before
so we are the first to get the rotation period for these bodies.

@@

%? TODO table of asteroids by class and frac that pass.

%TODO comp to LCDB
\red{57426 total, 1530 in LCDB, 868 of those pass check, 581 within 5 percent of y=2x, 28 within 5 percent of y=x}
